Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-02-21 response_to_review_SOLA-D-20-00015_v1.txt

-----------------------------------------------------------------------------------------
6. The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results. In particular: the results of the energy balance analysis and the estimate of energy flux at the coronal base, which are important.

(TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).

-----------------------------------------------------------------------------------------
7. Page 5, paragraph beginning line 34. You briefly describe fitting the DEM to a Gaussian. I know this approach is covered in detail in Nuevo 2015, but I would like a little more detail here. You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract ). Then explain briefly why DEMT leads to cleaner, non-multithermal profiles (due to the 3D spatial reconstruction of the line of sight). I assume that this is why you can use a straightforward Gaussian fit? Also efficiency?

Thanks for this comment and the references. As the LDEM describes the temeprature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS). In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies. Still, if one adds tbhe 335 A channel, which adds two sensitivity poits at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predics all the tomographic emissivities. That is the main conclusion of Nuevo et. al. (2015). The interpretation in that case is that the unresolved independent strands threading the voxel can have two different characteristic temperatures. Nuevo et al. (2015). So in this sense, the plasma within the voxel can be multi-thermal. As for efficiency, the parametric technique is comparably efficient independently of the chosen model. We did read the  We expanded this discussion in the text.

### 2020-03-04 lloveras_2020.tex
nuevas figuras

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
\label{carmaps_demt_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: {electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, {and loop-averaged temperature $\aTm$. In each panel} the median value $m$ is indicated.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$. Dashed and solid lines indicate AWSoM and DEMT results, respectively. Vertical black lines indicate the longitude-averaged latitude of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
\caption{Same as Figure \ref{histos_2082} for CR-2208.}
\label{histos_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_multistart2_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
\label{carmaps_demt_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}

\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustene_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajustelambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_conajusteTm.eps}
\caption{{Statistical distribution of {DEMT results for rotations CR-2082 (blue) and CR-2208 (red)} traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: {electron density $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$,} electron density scale height $\lN$, {and loop-averaged temperature $\aTm$. In each panel} the median value $m$ is indicated.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_multistart2_1105.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_multistart2_1105.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$. Dashed and solid lines indicate AWSoM and DEMT results, respectively. Vertical black lines indicate the longitude-averaged latitude of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_conajuste_Tm.eps}
\caption{Same as Figure \ref{histos_2082} for CR-2208.}
\label{histos_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_conajuste.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}
